A Stochastic Quasi-Newton Optimizer for \texttt{TensorFlow}

### 2018-05-01 presentation/main.tex
More updates
Presentation

\documentclass[draft]{beamer}

@@

\begin{frame}[t]{Our contribution}
  \begin{itemize}
    \item We implemented stochastic L-BFGS in \texttt{TensorFlow} following the
      work of Wang, Ma, Goldfarb, and Liu (2017).
    \item The approach is based on the iteration step:
      \[
        x_{k+1} = x_k - \alpha_k H_k g_k,
      \]
    \item $\alpha_k$ is the step size,
    \item $H_k$ is the L-BFGS approximate Hessian,
    \item $g_k$ is a batch gradient defined as
      \begin{equation*}
        g_k = \frac{1}{m_k} \sum_{i=1}^{m_k} g(x_k, \xi_{k,i}),
      \end{equation*}
    \item $m_k$ is the batch size,
    \item $\xi_{k,i}$ is randomly sampled training data.
  \end{itemize}
\end{frame}

\begin{frame}[t]{Our contribution}
  \begin{itemize}
    \item The specific approach to approximating the Hessian differs from
      traditional L-BFGS implementations.
    \item Wang, et al showed that convergence (in expectation) is guaranteed by
      applying dampening at specific places in the approximation.
    \item Crucially, this holds even if the problem is \textbf{non-convex}.
    \item Their update, \texttt{SdLBFGS}, 
  \end{itemize}<++>

\end{frame}<++>

@@

>>>>

\documentclass{beamer}

@@

\begin{frame}[t]{Our contribution}
  \begin{itemize}
    \item We implemented stochastic dampened (Sd) L-BFGS in \texttt{TensorFlow} following the
      work of Wang, Ma, Goldfarb, and Liu (2017).
    \item The approach is based on the iteration step:
      \[
        x_{k+1} = x_k - \alpha_k H_k g_k,
      \]
    \item $\alpha_k$ is the step size,
    \item $H_k$ is the L-BFGS approximate Hessian,
    \item $g_k$ is a batch gradient defined as
      \begin{equation*}
        g_k = \frac{1}{m_k} \sum_{i=1}^{m_k} g(x_k, \xi_{k,i}),
      \end{equation*}
    \item $m_k$ is the batch size,
    \item $\xi_{k,i}$ is randomly sampled training data.
  \end{itemize}
\end{frame}

\begin{frame}[t]{Our contribution}
  \begin{itemize}
    \item The specific approach to approximating the Hessian differs from
      traditional L-BFGS implementations.
    \item Wang, et al showed that convergence (in expectation) is guaranteed by
      applying dampening at specific places in the approximation.
    \item Crucially, this holds even if the problem is \textbf{non-convex}.
    \item Their update, \texttt{SdLBFGS}, preserves the positive-definiteness of
      $H_k$ even in non-convex situations.
  \end{itemize}
\end{frame}

@@

\begin{frame}[t]{Results: sanity checks}
  \includegraphics[width=\textwidth]{../plots/sanity_checks.eps} 
  \begin{itemize}
    \item Since our code is in \texttt{NumPy}, we could test it by running
      familiar homework functions.
    \item Here all gradients are deterministic.
  \end{itemize}
\end{frame}

\begin{frame}[t]{Results: Higgs dataset}
  \includegraphics[width=\textwidth]{../plots/higgs_dataset.eps} 
\end{frame}

\begin{frame}

\end{frame}
